---
title: "R Notebook"
output: html_notebook
---

```{r}
library(keyring)
library(RPostgreSQL)
keyring_unlock("local")
username <- key_get(service = "postgresql_username", keyring = "local") 
username <- "richardmichaelclark"
password <- key_get(service = "postgresql_password", keyring = "local")
keyring_lock("local")
db_connect <- dbConnect(drv = PostgreSQL(), user = username, password = password, dbname = "acme_employees", host = "localhost")
rm(username, password)
```

```{r}
data <- dbGetQuery(conn = db_connect, statement = "SELECT * FROM employees")
```


```{r}
dbGetQuery(db_connect,
           "SELECT * FROM employees
           ")
```

I cannot get this to work so I will write down my findings and the code I thing would have worked. I justy don't know what I have done wrong and I have been working (going round in circles since Friday night) 


Employees: id (primary key), first_name, last_name, email, team_id (foreign key)

Feedbacks: id (primary key), employee_id (foreign key), message, date

Teams: id (primary), name, charge cost

```{r}
dbGetQuery(db_connect,
           "SELECT * FROM employees
           CONCAT 'first_name', ' ', 'last_name'
           FROM employees AS 'full_name'")
```

```{r}
dbGetQuery(db_connect,
           "SELECT * FROM employees
           WHERE team_id AS team_name")
```

```{r}
dbGetQuery(db_connect,
           "SELECT team_name, COUNT(id) AS number_of_employees
           order by number_of_employees DESC")
```

```{r}
dbGetQuery(db_connect,
           "SELECT id
           WHERE email IS NULL AND 
           WHERE IS NOT LIKE '%@%'")
```








```{r}
dbDisconnect(db_connect)
```

