---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```
Purrrrrrrrrrrrrrrrrrrrrrr

map() is the main one.

Iterates over a data structure and runs a function that you provide on each "element" of the data structure. replaces 'for' loops.

map_<something>()
<something> is data type they return
e.g. map_dbl() return a vector that contains doubles i.e. numerical

```{r}
colour_feelings <- list(
    blue   = c("Sad", "Calm"),
    red    = c("Angry", "Energetic", "Warm"),
    green  = c("Calm", "Nature"),
    yellow = c("Happy", "Warm", "Sunny")
)
```

list on which each element is a character vector.

```{r}
colour_feelings$blue
```

```{r}
for(item in colour_feelings){
  print(length(item))
}
```

```{r}
map(.x = colour_feelings, .f = length)
```

```{r}
# pass extra arguments after .f
map(.x = colour_feelings, .f = paste, collapse = ", ")
```

```{r}
colour_translator <- list(
  blue   = "gorm",
    red    = "dearg",   
    green  = "uaine",
    yellow = "buidhe"   
)

```

We want to paste "Translation: " in front of each of these words

```{r}
add_translation <- function(text){
  return(paste("Translation: ", text))
}
```

```{r}
add_translation("gorm")
```

```{r}
map(.x = colour_translator, .f = add_translation)
```

purrr let's you define little "bespoke" custom-fitted functions to do wrangling.

```{r}
map(.x = colour_translator, .f = ~ paste("Transalation: ", .x))
```

dataframes in R are just lists where each element is a vector and the label of the element is like the column head.

```{r}
library(CodeClanData)
```

```{r}
colour_wavelengths <- list(
    blue   = 470,
    red    = 665,
    green  = 550,
    yellow = 600
)
```

```{r}
map(colour_translator, nchar)
```

```{r}
map(colour_wavelengths, round, digits = -2)
```

```{r}
map(colour_wavelengths, ~ .x/(1*(10^9)))
# 1E9 is scientific notation is 1 * 10^9
```

```{r}
#colour_feelings
map_dbl(colour_feelings, length)
```

```{r}
map_int(colour_feelings, length)
```

```{r}
flatten_chr(colour_feelings)
```

```{r}
studentslist <- as.list(students)
students
```

```{r}
students <- map_df(students, sort)
```

conditional mapping:

```{r}
blue <- list(
    translation = "gorm",
    feelings    = c("Sad", "Calm"),
    primary     = "Yes",
    wavelength  = 470
)
```

```{r}
# p is a predicate = logical i.e. condition/question
map_if(.x = blue, .p = is.character, .f = nchar)
```

```{r}
# apply paste only to elements of blue with a length > 1

map_if(.x = blue, .p = ~ length(.x) > 1, .f = paste, collapse = ", ")
```

```{r}
str(colour_list)
```

```{r}
map(colour_list, "wavelength")
```

```{r}
map(colour_list, "feelings")
```
# not the best way of doing things
```{r}
map(colour_list, 4)
```

```{r}
colour_list_feelings <- map(colour_list, "feelings")
map(colour_list_feelings, length)
```

API application programming interface
APIs return JSON javascript object notation
R converts json to nested list

Colours and themes

http://sape.inf.usi.ch/quick-reference/ggplot2/colour

Also look up hexidecimal colours

```{r}
ggplot(students) +
  aes(x = reaction_time) +
  geom_histogram(fill = "magenta")
```

```{r}
ggplot(students) +
  aes(x = reaction_time) +
  geom_histogram(fill = hcl(200, 50, 50))
```

```{r}
ggplot(students) +
  aes(x = reaction_time, y = height_cm) +
  geom_point(colour = "violetred1")
```


```{r}
ggplot(pets, aes(weight, age, colour = sex)) +
  geom_point()
```

```{r}
ggplot(pets, aes(weight, age, colour = sleep)) +
  geom_point() +
  scale_colour_gradient(low = "grey0", high = "grey100")
```
if colour is fill then scale is fill (make sense?)

```{r}
ggplot(pets, aes(weight, age, colour = sleep)) +
  geom_point() +
  scale_colour_gradient(low = "seagreen2", high = "turquoise4")
```

```{r}
ggplot(pets, aes(weight, age, colour = sleep)) +
  geom_point() +
  scale_colour_gradient2(low = "blue", high = "red", mid = "white", midpoint = 15)
```


Geom_raster is a heat map
```{r}
ggplot(volcano, aes(x = x, y = y, fill = height)) +
  geom_raster() +
  scale_fill_gradientn(colours = c("chartreuse1", "maroon1"))
  
```

```{r}
ggplot(volcano, aes(x = x, y = y, fill = height)) +
  geom_raster() +
  scale_fill_gradientn(colours = colorspace::terrain_hcl(10))
```

https://colorbrewer2.org/#type=sequential&scheme=OrRd&n=3

```{r}
ggplot(volcano, aes(x = x, y = y, fill = height)) +
  geom_raster() +
  scale_fill_distiller(palette = "OrRd")
```

```{r}
ggplot(temp_df) +
  geom_raster(aes(x = month, y = year, fill = max_temp)) +
  scale_fill_gradient(low = "olivedrab2", high = "darkorchid2")
```

```{r}
ggplot(temp_df) +
  geom_raster(aes(x = month, y = year, fill = max_temp)) +
  scale_fill_gradient2(low = "dodgerblue4", high = "deeppink4", mid = "darkorange2", midpoint = 10)
```

```{r}
ggplot(temp_df) +
  geom_raster(aes(x = month, y = year, fill = max_temp)) +
  scale_fill_gradientn(colours = colorspace::terrain_hcl(28))
```

```{r}
ggplot(temp_df) +
  geom_raster(aes(x = month, y = year, fill = max_temp)) +
  scale_fill_distiller(palette = "Dark2")
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar()
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
scale_fill_hue(h = c(120, 300))
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
  scale_fill_brewer(palette = "Set1")
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
  scale_fill_grey()
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
  scale_fill_grey(start = 0, end = 0.5)
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
  scale_fill_manual(values = c(
    "Fly" = "red",
    "Freeze time" = "blue",
    "Invisibility" = "green",
    "Telepathy" = "yellow"
  ))
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
  scale_fill_manual(values = c("red", "blue", "green", "yellow"))
```

```{r}
ggplot(students) +
  aes(x = school_year, fill = superpower) +
  geom_bar() +
  scale_fill_manual(values = wes_palette("GrandBudapest1"))
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line()
```



```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_hue(h = c(60, 2000))
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_grey(start = 0, end = 0.7)
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_brewer(palette = "Accent")
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_manual(values = c("red", "blue", "green", "orange"))
```

guide_colour_bar for continuous data

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_hue(guide = guide_legend(nrow = 3))
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_hue(guide = guide_legend(reverse = TRUE))
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  scale_colour_hue(guide = guide_legend(keywidth = 1, keyheight = 6, reverse = TRUE))
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  theme_grey(base_size = 20)
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  labs(
    title = "Typical Diet of a Chinese Citizen"
  ) +
  theme(
    title = element_text(size = 20, colour = "red", face = "bold")
  )
```

```{r}
?theme
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  labs(
    title = "Typical Diet of a Chinese Citizen"
  ) +
  theme(
    axis.title.x = element_text(size = 20, colour = "red", face = "bold"),
    panel.grid.major = element_line(colour = "black", linetype = "dotted", size = 0.3),
    plot.background = element_rect(fill = "limegreen")
  )
```

```{r}
ggplot(chinesemeal) +
  aes(x = Year, colour = FoodType, y = CaloriesPerDay) +
  geom_line() +
  labs(
    title = "Typical Diet of a Chinese Citizen"
  ) +
  theme(
    axis.title.x = element_text(size = 20, colour = "red", face = "bold"),
    panel.grid.major = element_line(colour = "black", linetype = "dotted", size = 0.3),
    plot.background = element_rect(fill = "limegreen"),
    legend.text = element_blank()
  )
```

```{r}
install.packages("ggthemes")
```

```{r}
library(ggthemes)
```

```{r}
ggplot(scottish_exports) +
  geom_line(aes(x = year, y = exports, colour = sector)) +
  facet_wrap(~sector, scales = 'free_y') +
  theme_excel() +
  theme(
    axis.title.x = element_text(size = 20, colour = "blue", face = "bold"),
    axis.title.y = element_text(size = 20, colour = "blue", face = "bold")
  )
```

Change order:
make into ordered factor
```{r}
total_sales %>% 
  mutate(branch = factor(branch, levels = c("London", "leeds", "Glasgow", "Leatherhed", "Edinburgh", "Manchester", "Welyn Garden City")))

ggplot(total_sales) +
  aes(x = branch, y = sales) +
  geom_col() +
  coord_flip()
```

```{r}
total_sales <- total_sales %>% 
  mutate(branch = fct_reorder(branch, sales))

ggplot(total_sales) +
  aes(x = branch, y = sales) +
  geom_col() +
  coord_flip()
```











