---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(modelr)
library(ggiraphExtra)
library(GGally)
```

```{r}
kc_house <- read_csv("data/kc_house_data.csv")
```

```{r}
kc_house
```

```{r}
summary(kc_house)
```

Removal of some variable names

```{r}
kc_trim <- kc_house %>% 
  select(-c(date, id, sqft_living15, sqft_lot15, zipcode))
```



```{r}
kc_trim
```

looking at "Waterfront" it's currently 1 or 0. I could change this to true or false or leave as is. As it is numeric and it's easier to model using numbers, I will keep as is.

I am going to convert yr_renovated into "renovated", a logical variable with a numerical form. 1 for having been revoated and 0 if not.

```{r}
kc_trim_dummy <- kc_trim %>% 
  mutate(renovated = ifelse(yr_renovated > 0, 1, 0)) %>% 
  select(-yr_renovated)
```

```{r}
kc_trim_dummy
```

Looking at variables condition and grade, I found this information:

https://rstudio-pubs-static.s3.amazonaws.com/155304_cc51f448116744069664b35e7762999f.html

grade - An index from 1 to 13, where 1-3 falls short of building construction and design, 7 has an average level of construction and design, and 11-13 have a high quality level of construction and design. 

condition - An index from 1 to 5 on the condition of the apartment, 

Therefore I am satisifed that they are sequential categorical ordinal data types.

Using the alias function, I will check for aliased variables:

```{r}
alias(lm, kc_trim_dummy)
```

```{r}
alias(price ~ condition, kc_trim_dummy)
```

```{r}
alias(price ~ bedrooms, kc_trim_dummy)
alias(price ~ bathrooms, kc_trim_dummy)
alias(price ~ sqft_living, kc_trim_dummy)
alias(price ~ sqft_lot, kc_trim_dummy)
alias(price ~ floors, kc_trim_dummy)
alias(price ~ waterfront, kc_trim_dummy)
alias(price ~ view, kc_trim_dummy)
alias(price ~ condition, kc_trim_dummy)
alias(price ~ grade, kc_trim_dummy)
alias(price ~ sqft_above, kc_trim_dummy)
alias(price ~ sqft_basement, kc_trim_dummy)
alias(price ~ yr_built, kc_trim_dummy)
alias(price ~ lat, kc_trim_dummy)
alias(price ~ long, kc_trim_dummy)
alias(price ~ renovated, kc_trim_dummy)
```

I cannot find a variable that leads to an alias so I haven't removed anything.

I will now consider building the regression model by examining what variables are strongly correlated to price.

```{r}
kc_trim_dummy %>% 
  ggpairs(aes())
```

As this impossible to read, I am going to split the variables by numeric and non-numeric.

```{r}
kc_trim_numeric <- kc_trim_dummy %>%
  select_if(is.numeric)

kc_trim_nonnumeric <- kc_trim_dummy %>%
  select_if(function(x) !is.numeric(x))

kc_trim_nonnumeric$price <- kc_trim_dummy$price

ggpairs(kc_trim_numeric)
ggpairs(kc_trim_nonnumeric)
```

I cannot seem to see which variables have a strong indication of a strong correlation to "price". Hence I will build the model trying to use my commonsense.

```{r}
kc_mod1 <- lm(price ~ yr_built, data = kc_trim_dummy)
kc_mod1
```

```{r}
summary(kc_mod1)
```

OK the figure for R squared is very low so this has very correlation.


```{r}
kc_mod2 <- lm(price ~ bedrooms, data = kc_trim_dummy)
kc_mod2
summary(kc_mod2)
```

```{r}
kc_mod3 <- lm(price ~ bathrooms, data = kc_trim_dummy)
kc_mod3
summary(kc_mod3)
```

Bathrooms had a higher R squared comparison % bit still quite low.

```{r}
kc_mod4 <- lm(price ~ sqft_living, data = kc_trim_dummy)
kc_mod4
summary(kc_mod4)
```

sqft_living is higher again at 0.49 R-squared.

```{r}
kc_mod5 <- lm(price ~ sqft_lot, data = kc_trim_dummy)
kc_mod5
summary(kc_mod5)
```

Again this is low

```{r}
kc_mod6 <- lm(price ~ floors, data = kc_trim_dummy)
kc_mod6
summary(kc_mod6)
```

```{r}
kc_mod7 <- lm(price ~ waterfront, data = kc_trim_dummy)
kc_mod7
summary(kc_mod7)
```

```{r}
kc_mod8 <- lm(price ~ view, data = kc_trim_dummy)
kc_mod8
summary(kc_mod8)
```

```{r}
kc_mod9 <- lm(price ~ condition, data = kc_trim_dummy)
kc_mod9
summary(kc_mod9)
```

```{r}
kc_mod10 <- lm(price ~ grade, data = kc_trim_dummy)
kc_mod10
summary(kc_mod10)
```

Grade is a bit more correlated.

```{r}
kc_mod11 <- lm(price ~ sqft_above, data = kc_trim_dummy)
kc_mod11
summary(kc_mod11)
```

```{r}
kc_mod12 <- lm(price ~ sqft_basement, data = kc_trim_dummy)
kc_mod12
summary(kc_mod12)
```

```{r}
kc_mod13 <- lm(price ~ yr_built, data = kc_trim_dummy)
kc_mod13
summary(kc_mod13)
```

```{r}
kc_mod14 <- lm(price ~ lat, data = kc_trim_dummy)
kc_mod14
summary(kc_mod14)
```

```{r}
kc_mod15 <- lm(price ~ long, data = kc_trim_dummy)
kc_mod15
summary(kc_mod15)
```

```{r}
kc_mod16 <- lm(price ~ renovated, data = kc_trim_dummy)
kc_mod16
summary(kc_mod16)
```
These 3 have the best indications

kc_mod11, sqft_above R-squared: 0.3667
kc_mod10, grade R-squared: 0.4454
kc_mod4, sqft_living R-squared 0.4928

```{r}
par(mfrow = c(2, 2))
plot(kc_mod4)
```

kc_mod4 doesn't look good at all. There is a trend on the "Scale-location" and on the "Normal" it doesn't follow the dotted line.

```{r}
par(mfrow = c(2, 2))
plot(kc_mod10)
```

kc_mod10 also doesn't follow the normal posting properly.

```{r}
par(mfrow = c(2, 2))
plot(kc_mod11)
```

kc_mod11 doesn't fare much better.

```{r}
kc_mod17 <- lm(price ~ sqft_living + grade, data = kc_trim_dummy)
summary(kc_mod17)
```

This is better yet.

```{r}
kc_mod18 <- lm(price ~ sqft_living + grade + sqft_above, data = kc_trim_dummy)
summary(kc_mod18)
```

```{r}
anova(kc_mod18)
```

All 3 are siginifcantly impacting the price.

