---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
```

```{r}
avocado <- read_csv("data/avocado.csv")
avocado
```

I am checking here whether there is any missing values in the dataset. There are in fact zero N/A's - see below.

```{r}
summary(avocado)
```

```{r}
library(GGally)
```

In an effort to reduce the amount of variables, I am going to exclude index, the bag sizes (because we have no information about how much they hold), the year and the region. I am going to add two variables: month (to try to correlate any cyclical element to average price), other_avocados: for the the remainder avocados not listed under the 3 PLU codes.

```{r}
library(lubridate)
```
```{r}
library(janitor)
```

```{r}
avocado <- clean_names(avocado)
```

```{r}
avocado
```


```{r}
avocado_trim <- avocado %>% 
  mutate(month = month(date)) %>% 
  mutate(other_avocados = (total_volume - (x4046 + x4225 + x4770))) %>% 
  select(month, average_price, x4046, x4225, x4770, other_avocados, type, month)
```

```{r}
avocado_trim
```

Now I will plot some visualisation to see if I can identify some variable relationships for average_price

```{r}
ggpairs(avocado_trim)
```

Looking at the R squared values here, it would appear that month has the greatest correlation to average price so this is where we shall start.

```{r}
avocado_trim %>% 
  ggplot(aes(x = month, y = average_price)) +
  geom_point() +
  geom_smooth()
```

The graph above is not conclusive because prices seem to stretch up and down but there is a suggestion that apart from some outliers, average price peaks around the end of summer (Aug) to early Autumn (Sep/Oct)

So I will build the model with average price and month

```{r}
avocado_mod1 <- lm(average_price ~ month, data = avocado_trim)
```

```{r}
summary(avocado_mod1)
```

The R squared figure isn't high but it wasn't when we originally plotted it. 

I will now plot against the regression comparisons.

Residuals vs fitted is around nil which is correct. Normal Q-Q is following the dotted line which is also a good correlation. Scale-Location is relatively flat which is also good and not indicating a trend.

```{r}
par(mfrow = c(2,2))
plot(avocado_mod1)
```

Looking back again at the GGpairs data, type doesn't appear to have any bearing as the box plot indicates no difference in whether organic or not.

I am inclined to add all the avocado PLU's together (but separate) into the model to distinguinsdh between them.

```{r}
avocado_mod2 <- lm(average_price ~ month + x4046 + x4225 + x4770 + other_avocados, data = avocado_trim)
```

```{r}
summary(avocado_mod2)
```

This would indicate "other avocados" is not significant so I will delete that for model 3.

```{r}
avocado_mod3 <- lm(average_price ~ month + x4046 + x4225 + x4770, data = avocado_trim)

summary(avocado_mod3)
```

```{r}
par(mfrow = c(2,2))
plot(avocado_mod3)
```

Unfortunately model 3 does not show peomise with the residulas vs fotted as the trend is moving away from nil. The scale location has a definite trend downwards which is also not helpful. The Mormal Q-Q graph follows the odtted line.

Therefore model 1: avocado_mod1 <- lm(average_price ~ month, data = avocado_trim) appears to be the most accurate.

And here are answer to the quiz on regaressionn models:

1. overfitting
2. the one with the score of 33,559
3. the one with an adjusted r squared value of 0.43
4. No
5. it goes through each iteration testing one and using the rest as control subjects.
6. It's a data set that has been cleaned for use in the refgrssion analysis
7. 
8.
9. Keep it simple, make it as uncomplicated as possible, include commentary and justifciation
10. log
11. 
12.
13.
14.
15.
16. To show that you are applying your knowledge and adding value



























