---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(tidyverse)
library(janitor)
library(e1071)
library(skimr)
```

```{r}
mob_shop <- read_csv("data/20190928-items.csv")

mob_shop
```

```{r}
colnames(mob_shop, do.NULL = TRUE, prefix = "col")
```

```{r}
mob_shop <- clean_names(mob_shop)
```

```{r}
mob_shop %>% 
  group_by(brand) %>% 
  summarise()
```

```{r}
mob_brands <- c("Apple", "ASUS", "Google", "HUAWEI",	"Motorola", "Nokia", "OnePlus", "Samsung", "Sony", "Xiaomi")
```

```{r}
mob_shop %>% 
  group_by(brand) %>% 
  count()
```

The most popular brand in this dataset is Samsung

```{r}
samsung_mob <- mob_shop %>% 
  filter(brand == "Samsung")

samsung_mob
```

```{r}
getMode <- function(data){
  tabled_data <- table(data)
  table_names <- names(tabled_data)
  return( table_names[tabled_data == max(tabled_data)] )
}
```

```{r}
samsung_mob %>% 
  skim(rating)
```

Looking at the figures here we can expect this to be left skewed as majority of ratings are 3.3 through to 5 score. The standard deviation is less than 1 which is low variance.

```{r}
samsung_mob %>% 
  summarise(mode_samsung_rating = getMode(rating))
```
The mode is very similar to the mean and exactly the same as the median making the mean a good calculation.


```{r}
samsung_mob %>% 
  ggplot(aes(y = rating)) +
  geom_boxplot()
```
There are a few outliers in the lower end of the scoring.


```{r}
library(MASS)
```

```{r}
samsung_mob %>% 
  fitdistr(x = rating)
```

```{r}
samsung_mob %>% 
  ggplot(aes(x = rating, bins = 25)) +
  geom_histogram()
  
```

```{r}
samsung_mob %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 30) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = 3.57, 
      sd = 0.685
    ),
    col = "red"
  )
```

The distribution fits the graph reasonably well. It would appear there may be two modes.

```{r}
samsung_mob %>% 
  group_by(rating) %>% 
  count() %>% 
  arrange(desc(n))
```

However you can clearly see that is not the case.

```{r}
samsung_mob_rat <- samsung_mob %>% 
  dplyr::select(rating)
```

```{r}
samsung_mob_rat %>%
  filter(rating >= 3.57 - 0.685) %>%
  filter(rating <= 3.57 + 0.685) %>%
  summarise(prop_within_1sd = n() / nrow(samsung_mob_rat))
```

```{r}
samsung_mob %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 30) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = 3.57, 
      sd = 0.7934509
    ),
    col = "red"
  )
```



```{r}
samsung_mob_rat %>%
  filter(rating >= 3.57 - 2 * 0.685) %>%
  filter(rating <= 3.57 + 2 * 0.685) %>%
  summarise(prop_within_2sd = n() / nrow(samsung_mob_rat))
```


```{r}
samsung_mob %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 30) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = 3.57, 
      sd = 0.9219144
    ),
    col = "red"
  )
```




```{r}
samsung_mob_rat %>%
  filter(rating >= 3.57 - 3 * 0.685) %>%
  filter(rating <= 3.57 + 3 * 0.685) %>%
  summarise(prop_within_3sd = n() / nrow(samsung_mob_rat))
```

```{r}
samsung_mob %>% 
  ggplot(aes(x = rating)) +
  geom_histogram(aes(y = ..density..), col = "white", bins = 30) +
  stat_function(
    fun = dnorm, 
    args = list(
      mean = 3.57, 
      sd = 0.9798489
    ),
    col = "red"
  )
```

