---
title: "R Notebook"
output: html_notebook
---

```{r}
library(dplyr)
library(lubridate)
library(tidyverse)
library(tsibble)
library(tsibbledata)
library(feasts)
date1 <- ymd_hms("2017-04-22 22:01:18")
date2 <- ymd_hms("2001-11-07 10:09:56")
```

```{r}
library(nycflights13)
```

Question1.

```{r}
year(date1)
month(date1)
mday(date1)
yday(date1)
wday(date1)

date1
```

Q2.

```{r}
next_fortnight <- date1 + days(14)

next_fortnight

previous_decade <- date2 - years(10)

previous_decade
```

Question 3.

```{r}
this_year <- ymd("2020-04-20")
```

```{r}
this_year
```

```{r}
interval_years <- lubridate::interval(ymd(this_year), date(previous_decade))
```

Question 4.

```{r}
nyc_date1 <-with_tz(date1, tz = "America/New_York")
```

```{r}
nyc_date2 <-with_tz(date2, tz = "America/New_York")
```

Question 5.

```{r}
flights
```

```{r}
flights %>% 
  mutate(departure_date = make_datetime(year, month, day, hour, minute))
```

Question 6.

```{r}
weather
```

```{r}
weather %>% 
  select(temp, humid, precip, time_hour)
```

temp = temperature
humid = humidity
precip = precipitation
time_hour is the index which derives its numbers from the key variables: year, month, day and hour

```{r}
?as.tsibble()
```


```{r}
duplicates(weather)
```


```{r}
(weather) %>% 
  tsibble::as_tsibble(index = time_hour, regular = FALSE)
```

Strggling to turn it into a tsibble

Q8.

```{r}
weather_1 <- weather %>% 
  select(temp, humid, precip, time_hour) %>% 
  mutate(year = year(time_hour)) %>% 
  mutate(month = month(time_hour))
```

```{r}
weather_1 %>% 
  ggplot(aes(x = time_hour, y = temp)) +
  geom_line()
```

I can group it by daily observations for something more accurate

Question 9.

```{r}
temp_rolling <- weather_1 %>% 
  mutate(temp_moving_average = slide_dbl(temp,
                                         ~ mean(., na.rm = TRUE),
                                         .size = 1000))

ggplot(temp_rolling) + 
  geom_line(aes(x = time_hour, y = temp), colour = "grey") +
  geom_line(aes(x = time_hour, y = temp_moving_average), colour = "blue")
  
```
I chose this time window as it looked good. Temperatures are cyclical, peaking in August in the year.


```{r}
weather %>% 
  filter(airports %in% c("Queensland", "New South Wales", "Victoria")) %>% 
  gg_subseries(temp))
  
```
I cannot find the airports in the weather tibble. What is above is an example if it was there.



