---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
data(msleep)
library(janitor)
library(infer)
library(skimr)
```

Question 1.1

```{r}
glimpse(msleep)
```

```{r}
msleep <- clean_names(msleep)
```

```{r}
glimpse(msleep)
```

```{r}
msleep
```

```{r}
msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))
```

```{r}
mean_sleep_total <- msleep %>% 
  summarise(mean_sleep_total = mean(sleep_total))
```

```{r}
jabber_wock_sleep <- 7.00
```

```{r}
per_cent_less_jabb_sleep <- (jabber_wock_sleep - mean_sleep_total) / mean_sleep_total

per_cent_less_jabb_sleep
```



The mean sleep total is much greater than the mean for Jabberwockies. They sleep for 32.9% less per night than the average for other animals.

```{r}
msleep %>% 
  filter(vore == "herbi") %>% 
  summarise(mean_sleep_herbi = mean(sleep_total))
```

```{r}
msleep %>% 
  filter(vore == "omni") %>% 
  summarise(mean_sleep_omni = mean(sleep_total))
```

```{r}
mean_sleep_herbi <- msleep %>% 
  filter(vore == "herbi") %>% 
  summarise(mean_sleep_herbi = mean(sleep_total))

mean_sleep_omni <- msleep %>% 
  filter(vore == "omni") %>% 
  summarise(mean_sleep_omni = mean(sleep_total))

(mean_sleep_omni - mean_sleep_herbi) / mean_sleep_omni
```

Omnivores sleep on average 13.0% more tan Herbivores.

Determine whether the proportion of domesticated animal types in the population of animal types is greater than 5%.

First I mist add in a column that flahs whether the animal is domesticated


```{r}
sleep_domest <- msleep %>% 
  mutate(is_domesticated = conservation == "domesticated")
```

```{r}
sleep_domest
```

Now I am going to caluclate the proportion of animals that we know are domesticated.

```{r}
sleep_domest %>% 
  group_by(is_domesticated) %>% 
  summarise(prop = n() / nrow(msleep)) %>% 
  filter(is_domesticated == TRUE)
```

In this datset the proportion is 12.05% and is therefore greater than 5%.

Question 1.2



The coffee shop: Simulation

H0: (the null hypothesis) the current awareness of the coffee shop in the town is 40% which was the score after the first survey was completed

H0: π average awareness = 0.40

Ha: (the alternative hypothesis) is that after performing a marketing campaign flyering local venues and targeting adverts on social media, here has been increase in awareness in the town of your coffee shop.

Ha: π average awareness ≠ 0.40

As this is a proportional we would need a variable heading: "aware_of_coffee_shop" answer: "TRUE" OR "FALSE".

I would perform a  proportion calculation:

tibble %>% 
  group_by(aware_of_coffee_shop) %>% 
  summarise(prop = n()/nrow(tibble)) %>%
  filter(aware_of_coffee_shop == TRUE)

Then I would decide upon a significance level α "alpha" = 0.05 typically.

Next we calculate the statistic we are interested in:

Number of people aware of coffee shop in town / number of people in town asked from the new sample. 

Then we crate a sampling distribution for the null hypothesis  called the null sampling distribution.

Then we see where our statistic falls on the null sampling distribution, calculating the probability of getting a statistic equal to or greater than our observed value.

If the p value is less than or equal to α then we reject the null hypothesis in favour of the alternative hypothesis.

If the p-value is greater than α then we fail to reject the null hypothesis.

null_distribution <- tibble %>%
  specify(response = aware_of_coffee_shop, success = TRUE) %>% 
  hypothesize(null = "point", p = 0.45) %>% # let's say the new % is 45%
  generate(reps = 1000, type = "simulate") %>%
  calculate(stat = "prop")
  
null_distribution %>%
  visualise()
  
observed_stat <- tibble %>% 
  specify(response = aware_of_coffee_shop, success = TRUE) %>% 
  calculate(stat = "prop")

observed_stat

null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "right") # it;s right bewcause we're expecting it to be greater

p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "right")

p_value

Website Design A / B test - permutations

This is a hypothesis test with two independent samples where we are interested in the difference in proportions of each sample group that clicked through (clicked through rate: CTR)

H0 π banner at right - π banner at top = 0
Ha π banner at right - π banner at top ≠ 0

observed_stat <- banners %>% 
  specify(banner_type ~ click_through, success = "banner at top") %>% 
  calculate(stat = "diff in props", order = c("banner_right", "banner_top"))

observed_stat

null_distribution <- banner %>%
  specify(banner_type ~ click_through, success = "banner at top") %>% 
  hypothesize(null = "independence") %>% 
  generate(reps = 1000, type = "permute") %>%
  calculate(stat = "diff in props", order = c("banner_right", "banner_top"))

head(null_distribution)

null_distribution %>%
  visualise() +
  shade_p_value(obs_stat = observed_stat, direction = "both")

We say both because we don't which way it will go.

p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat, direction = "both")

p_value

Car Manufacturing Company Quality Control - bootsrap

H0 µ average width = 145mm
Ha µ average width ≠ 145mm

observed_stat <- car_parts %>%
  summarise(mean_size = mean(part_size))

observed_stat

null_distribution <- car_parts %>%
  specify(response = average_rating) %>%
  hypothesize(null = "point", mu = 145) %>%
  generate(reps = 10000, type = "bootstrap") %>%
  calculate(stat = "mean")
  
null_distribution %>%
  visualise(bins = 30)
  
  
null_distribution %>%
  visualise(bins = 30) +
  shade_p_value(obs_stat = observed_stat$mean_rating, direction = "both")
  
p_value <- null_distribution %>%
  get_p_value(obs_stat = observed_stat$mean_size, direction = "both")
p_value

Q1.2.2.

Coffee shop: Significance level: 0.05, calculated p-value: 0.07 - p value is greater so we fail to reject the null hypothesis

Website company problem. Significance level: 0.01, p-value: 0.006 - p value is lower than alpha so we reject the null hypothesis in favour of the laternative hypothesis

Manufacturing company problem. Significance level: 0.05, p-value: 0.55 - p value is greater so we fail to reject the null hypthesis.









