---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(lubridate)
library(tsibble)
library(tsibbledata)
library(fable)
```

```{r}
nyc_bikes
```

```{r}
names(nyc_bikes)
```

Question 1.

```{r}
nyc_bikes_times <- nyc_bikes %>% 
  mutate(year = year(start_time)) %>% 
  mutate(month = month(start_time)) %>% 
  mutate(date = date(start_time))

nyc_bikes_times
```

Question 2.

```{r}
nyc_bikes_index <- nyc_bikes_times %>% 
  index_by(month) %>% 
  summarise(monthly_bike_hire = n())

nyc_bikes_index
```

```{r}
nyc_bikes_index %>% 
  ggplot(aes(x = month, y = monthly_bike_hire)) +
  geom_line()
```
This isn't very much data by which to come up with a forecast. it is only one calendar year and shows a seasonal variation in one iteration.


Question 3.

```{r}
nyc_bikes_date_index <- nyc_bikes_times %>% 
  index_by(date) %>% 
  summarise(daily_bike_hire = n())

nyc_bikes_date_index
```

```{r}
nyc_bikes_date_index %>% 
  ggplot(aes(x = date, y = daily_bike_hire)) +
  geom_line()
```

This might be OK for a monthly forecast but not for a quarter or year. Ideally we would need 2 - 3 years data.

Question 4.

```{r}
nyc_bikes_filled <- nyc_bikes_date_index %>%
  fill_gaps(daily_bike_hire = as.integer(median(daily_bike_hire)))
```



```{r}
nyc_fit <- nyc_bikes_filled %>% 
  filter_index("2018-01-01" ~ "2018-12-31")

nyc_forecast <- nyc_fit %>% 
  model(
    naive_model = NAIVE(daily_bike_hire),
    mean_model = MEAN(daily_bike_hire),
    snaive_model = SNAIVE(daily_bike_hire)
  )

nyc_forecast_2019 <- nyc_forecast %>% 
  forecast(h = 120)
```

```{r}
nyc_forecast_2019
```

Question 5.

```{r}
nyc_forecast_2019 %>% 
  autoplot(nyc_fit, level = NULL)
```

Question 6.

```{r}
nyc_accuracy_model <- nyc_forecast_2019 %>% 
  accuracy(nyc_bikes_filled)

nyc_accuracy_model %>% 
  arrange(RMSE)
```

Question 7.

I am not entirely sure what my testing of the model proved or if I have done it correctly.

I don't think the forecast is terribly accurate as there was a gradual trend upwards in the same period the prior year.

I would like more data but I would also like to use a different model that mirrored the cyclical element of the year 

Question 8.

```{r}
nyc_bikes_filled
```

```{r}
nyc_bikes_times
```


```{r}
nyc_bikes_spatial <- nyc_bikes_times %>% 
  mutate(end_month = month(stop_time))

```

```{r}
nyc_bike_spatial_adj <- nyc_bike_spatial %>% 
  select(bike_id, start_lat, start_long, end_lat, end_long, date, end_month)
```

```{r}
nyc_bike_spatial_adj %>% 
  ggplot(aes(x = start_lat, y = start_long, colour = date)) +
  facet_wrap(~bike_id) +
  geom_point() +
  ggtitle("Start Points")
```

```{r}
nyc_bike_spatial_adj %>% 
  ggplot(aes(x = end_lat, y = end_long, colour = date)) +
  facet_wrap(~bike_id) +
  geom_point() +
  ggtitle("Finish Points")
```

```{r}
library(leaflet)
```

```{r}
nyc_bike_spatial_adj %>% 
  leaflet() %>% 
  addTiles() %>% 
  addMarkers(
    lng = ~start_long,
    lat = ~start_lat
  )
```





























