---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(infer)
library(janitor)
```

```{r}
ames <- read_csv("data/ames.csv")
ames <- clean_names(ames)
glimpse(ames)
```

```{r}
ames %>% 
  ggplot(aes(x = sale_price)) +
  geom_histogram(col = "white")
```

The distribution has one peak but isn't particularly normal as it has one or two outliers and is skewed to the right.

```{r}

mean_ames <- ames %>% 
  summarise(
    mean_sale_price = mean(sale_price)
  )

mean_ames
```

```{r}
ames_sample_100 <- ames %>% 
  rep_sample_n(size = 100, reps = 1) %>% 
  ungroup() %>% 
  select(sale_price)

ames_sample_100
```




```{r}
bootstrap_ames_sample_100 <- ames_sample_100 %>% 
  specify(response = sale_price) %>% 
  generate(reps = 1000, type = "bootstrap") %>% 
  calculate(stat = "mean")

bootstrap_ames_sample_100
```

```{r}
results <- bootstrap_ames_sample_100 %>% 
  get_ci(level = 0.95, type = "percentile")

results
```

```{r}
results %>% 
  if(mean_ames >= "2.5%" & mean_ames <= "97.5%" %>% 
     mutate(popn_param_in_ci = "True")) 
  else("False")
```

The mean figure is 180,796 which is between the higher and lower amounts.

```{r}
bootstrap_ames_sample_100 %>% 
  visualise() +
  shade_confidence_interval(endpoints = results)
```

I haven't been able to create the tibble with the extra columns. I only have one row in the tibble. Is that wrong? Do you want the extar column in the original tibble?

The Bootstrap distribution is a bit more bell-shaped and normal.

```{r}
bootstrap_ames_sample_100 %>% 
  as_tibble() %>%
  mutate(popn_param_in_ci = "True" >= "2.5%" & <= "97.5%", "False")
```













































