---
title: "R Notebook"
output: html_notebook
---

```{r}
library(prob)
library(gtools)
library(tidyverse)
```
Question 1

```{r}


4/6
```

```{r}
s_one_dice <- rolldie(1)

total_one_dice <- nrow(s_one_dice)
```



```{r}
less_than_5 <- s_one_dice %>% 
  filter(X1 < 5)

less_than_5

total_less_than_5 <- nrow(less_than_5)
```

```{r}
prob_less_than_5 <- total_less_than_5 / total_one_dice

prob_less_than_5


```

Question 2.

```{r}
s_three_dice <- rolldie(3)

total_three_dice <- nrow(s_three_dice)
total_three_dice
```

Question 3.
(i)
```{r}
s_four_dice <- rolldie(4)
total_size_four <- nrow(s_four_dice)

total_5_6_7 <- s_four_dice %>% 
  filter(X1 + X2 + X3 + X4 == 5:7)
total_size_5_6_7 <- nrow(total_5_6_7)

total_size_four
total_size_5_6_7
```
Answer = 9

(ii)
```{r}
prob_5_6_7 <- 9 / 1296
prob_5_6_7
```

(iii) Ummm that doesn't make sense

Question 4.

Let's presume the heights are integers
This is the same calculation as 5! as the subset is the same as the number

```{r}
heights <- 1:5

order_heights <- as_tibble(permutations(n = 5,
                                     r = 5,
                                     v = heights,
                                     repeats.allowed = FALSE))
order_heights
```

Probability therefore is:

```{r}
1 / 120
```

Question 5.
(i)
```{r}
s_six_dice <- rolldie(6)
s_six_dice
```

```{r}
1 / 46656
```

(ii)
```{r}
six_dice <- 1:6

all_six_numbers <- as_tibble(permutations(n = 6,
                                        r = 6,
                                        v = six_dice,
                                        repeats.allowed = FALSE))
all_six_numbers
```

```{r}
1 / 720
```

Question 6.
As the question states it is the probablity that the card is spades as it's already stated it's black
```{r}
13/ 26
```

Question 7.
(i)
```{r}
patients <- c("Alice", "Bob", "Carmen", "Dinesh", "Ella", "Fergus", "Gianna", "Henry")

five_patients <- as_tibble(permutations(n = 8,
                                        r = 5,
                                        v = patients,
                                        repeats.allowed = FALSE))
five_patients
```

```{r}
?isin
```


(ii)
```{r}
gianna_dinesh_one <- isin(five_patients, "Gianna", ordered = FALSE)

sum(gianna_dinesh_one)
```

```{r}
gianna_dinesh_two <- isin(five_patients, "Dinesh", ordered = FALSE)

sum(gianna_dinesh_two)
```

```{r}
# ???
```

(iii) not saure how to answer this one

Question 8.
Let's give students letters A to H
```{r}
students <- c("A", "B", "C", "D", "E", "F", "G", "H")

five_student_quiz <- as_tibble(permutations(n = 8,
                                            r = 5,
                                            v = students,
                                            repeats.allowed = FALSE))
five_student_quiz
```

Answer 6,720






